Bayesian statistics and swine flu

### 2009-09-25 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@415 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

# graph hospital times
plotHospitals(hospSample)
@
\end{frame}

\begin{frame}[fragile]
\frametitle{With rising and falling incidence}
{\scrpitsize
<<hospLoad2,echo=T,height=2,width=4>>=
# generate hospital times
hospSample2 = simHospitals(paramSample , Ndays=80, 
	NinfectionsPerDay=c(seq(1, 100, len=20),seq(100, 1, len=20), rep(2, 40) ) )

# graph hospital times
plotHospitals(hospSample2)
@
}
\end{frame}

\begin{frame}
\frametitle{Age?}
\begin{itemize}
	\item Assume the fatality and hospitalization probabilities vary with age
	\item After data augmentation, we have a binary response with a smoothly-varying probability
	\item Use a canned Bayesian semi-parametric routine to generate a new age curve at every iteration.
	\item {\tt DPpackage}?
	\item Informative prior on the average or rate at a baseline age
	\item Strong prior that the curve is flat.
\end{itemize}
\end{frame}

>>>>

# graph hospital times
plotHospitals(hospSample)
abline(h=20)
@
\end{frame}

\begin{frame}[fragile]
\frametitle{With rising and falling incidence}
{\scriptsize
<<hospLoad2,echo=T,height=2,width=4>>=
# generate hospital times
Ninfect=	c(seq(1, 100, len=20),seq(100, 1, len=20), rep(2, 40) ) )

hospSample2 = simHospitals(paramSample , Ndays=80, NinfectionsPerDay=Ninfect)

# graph hospital times
plotHospitals(hospSample2)
lines(Ninfect)
@
}
\end{frame}
